%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Gadzhibala}{Pirmagomedov}{ \urlstyle{same}\url{http://gadzhibala.me} \\
\href{mailto:gadzhi@yandex.com.com}{gadzhi@yandex.com} | +7 928 508 57 07
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Dagestan State}
\subsection{Technical University}
\descript{Management \& Information \\ in Technical Systems}
\location{Expected Aug 2013 | \\ Mackhachkala, Russia}
\sectionsep

\subsection{The Internet Initiatives}
\subsection{Development Fund}
\descript{Acceleration Program for Start-Ups}
\location{May 2017 - Sep 2017 \\ Moscow, Russia}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/gadzhi}{\custombold{gadzhi}} \\
LinkedIn://  \href{https://www.linkedin.com/in/gadzhibala}{\custombold{gadzhibala}} \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Mathematics and Python for Data Analytics 
{\footnotesize \textit{\textbf{(Course Coursera) }}} \\
Introduce in Python {\footnotesize \textit{\textbf{(Course Stepic.org) }}} \\
Certificate of completion of the CIEE \\
{\footnotesize \textit{\textbf{(Work and Travel USA Program) }}}
\sectionsep

\subsection{Projects}
RestoBot (\href{https://restobot.io}{\custombold{link}}) \\
{\footnotesize \textit{\textbf{(Founder) }}} \\
Pyiiko (\href{https://github.com/gadzhi/pyiiko}{\custombold{link}}) \\
{\footnotesize \textit{\textbf{(Pyiiko is the easy-to-use library for iiko ERP.) }}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming:}
Python \textbullet{} SQL \textbullet{} Flask \textbullet{} pandas \\
\textbullet{} numpy \textbullet{} Git \textbullet{} XML \textbullet{} MongoDB \textbullet{} \\ 
\textbullet{} TelegramAPI \textbullet{} requests\\
\subsection{Administrating:}
Microsoft \& Linux Servers \textbullet{} Asterisk \textbullet{} Docker \textbullet{} Zabbix \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{RestoBot}
\descript{| Founder + Software Engineering}
\location{April 2017 - Present | Makhachkala, Russia}
RestoBot is an AI software for restaurant chains that is able to prevent fraud of the staff in the restaurant.
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Flask
\item pandas
\item SQL \& MongoDB
\item JSON \& XML
\end{tightemize}
\sectionsep

\runsubsection{Atrier}
\descript{| Python developer + System administrator}
\location{Sep 2014 – April 2017 | Mountain View, CA}
Development and implementation of iiko ERP products  and own products.
\begin{tightemize}
\item Develop programs to automate process of iiko ERP system and utilities using Python3
\item Develop Telegram bot on Python. This bot informs user about dangerous events in ERP system iiko (for restaurant and cafe), using iiko API. Also this bot informs revenue per day and the use of discounts.
\item Install and configure Web and Application Servers on Linux and the same procedure on MySQL.
\item Using Python library for data analysis (pandas, numpy).
\item Acquired massive savings for the company while creating new features, lines, and options without any additional cost through the installation and configuration of an Asterisk open-source VOIP system with an IVR and auto-attendant feature.
\item CentOS and Ubuntu server administered, Zabbix monitoring.
\end{tightemize}
\sectionsep

\runsubsection{Payment Processing Center}
\descript{| Network Administrator}
\location{Nov 2010 – Sep 2014 | Derbent, Russia}
Provided troubleshooting and timely resolutions for system hardware, software, and networking issues in a high volume utility services payment center.
\begin{tightemize}
\item Technical advice and training network and system administration (including an introductory course for Windows Server and Linux systems) 
\item Directs the administration and support of MS SQL servers for to account for the payment for utility services (30,000+ accounts), making report, every day backups, including performing monitoring and health checks of SQL Databases.
\item Minimized downtime by performing Addpac GSM Gateways (4 GSM) Configuration and Implementation as well as the successful integration with Asterisk.
\item Maintained TCP/IP LAN for 300+ Windows workstations with servers configured for Domain Controller, DNS, DHCP, Firewall.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Language}
\vspace{\topsep}
\begin{tightemize}
\item English
\item Russian
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2017	     & Resident  & Business incubator «PERI Innovation»
\\

\end{tabular}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}